---
title: "Analysis on Models with Contact & Communication Network Features"
author: "Coco Yu"
date: "`r lubridate::today()`"
format:
  html:
    toc: true 
    toc_depth: 4
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

### Setup

Chunk Defaults
```{r}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

suppressPackageStartupMessages(library(tidyposterior))
library(tidyverse)
library(tidymodels)
options(conflicts.policy = "depends.ok")
source("https://github.com/jjcurtin/lab_support/blob/main/fun_ml.R?raw=true")

library(kableExtra, exclude = "group_rows")
library(lubridate)
library(janitor, include.only = c("tabyl", "clean_names"))
library(Matrix, exclude = c("expand", "pack", "unpack"))
library(poissonreg)
library(DALEX, exclude= "explain")
library(DALEXtra)

theme_set(theme_classic()) 
```

Absolute Paths 
```{r}
source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/fun_plots.R?raw=true")
source("_lib/ana_models.R")

path_network <- format_path(str_c("risk/data_processed/network"))
path_models <- format_path(str_c("risk/models/network"))
```

### Read in Data

```{r}
err_tbl <- read_csv("_results/err_tbl_glmnet_v4.csv")

fits_lst <- read_rds(here::here(path_models, "fits_lst_glmnet_v4.rds"))

best_models <- read_rds(here::here(path_models, "best_models_glmnet_v4.rds"))

features_contacts <- read_csv(here::here(path_network, "features_network_v7.csv"))
features_communications <- read_csv(here::here(path_network, "features_network_v8.csv"))
features_contacts_communications <- features_contacts |> 
  left_join(features_communications, by = "subid")
labels <- read_csv(here::here(path_network, "labels.csv"))
features_baseline <- read_csv(here::here(path_network, "features_baseline.csv"))
```

```{r}
features_full <- features_contacts_communications |> 
  left_join(features_baseline, by = "subid") |> 
  left_join(labels, by = "subid") |>
  mutate(lapse = as.integer(n_lapse / day_on_study * 91)) |>
  select(-n_lapse, -day_on_study, -subid)

features_ablate_communications <- features_contacts |> 
  left_join(features_baseline, by = "subid") |> 
  left_join(labels, by = "subid") |>
  mutate(lapse = as.integer(n_lapse / day_on_study * 91)) |>
  select(-n_lapse, -day_on_study, -subid)

features_ablate_contacts <- features_communications |> 
  left_join(features_baseline, by = "subid") |> 
  left_join(labels, by = "subid") |>
  mutate(lapse = as.integer(n_lapse / day_on_study * 91)) |>
  select(-n_lapse, -day_on_study, -subid)

features_ablate_contacts_communications <- features_baseline |> 
  left_join(labels, by = "subid") |>
  mutate(lapse = as.integer(n_lapse / day_on_study * 91)) |>
  select(-n_lapse, -day_on_study, -subid)


```


### Best Models

COCO: name convention -> change full to id
combined to contacts_communications

ablating (unique variance) -> start with full model, ablate contacts only, then ablate communications only, ablate id only, ablate both contacts & communications

total variance -> contacts only, communications only, ID only(??)

```{r}
# best full model
id_full <- err_tbl |> 
  filter(feature_version == "features_combined_full") |> 
  arrange(desc(rsq_median)) |> 
  slice_head(n = 1) |> 
  pull(id) |> 
  as.numeric()

# ablate contacts
id_ablate_contacts <- err_tbl |> 
  filter(feature_version == "features_communications_full") |> 
  arrange(desc(rsq_median)) |> 
	slice_head(n = 1) |> 
	pull(id) |> 
	as.numeric()

# ablate communications
id_ablate_communications <- err_tbl |>
  filter(feature_version == "features_contacts_full") |> 
  arrange(desc(rsq_median)) |> 
	slice_head(n = 1) |> 
	pull(id) |> 
	as.numeric()

# ablate contacts & communications
id_ablate_contacts_communications <- err_tbl |> 
  filter(feature_version == "features_baseline") |> 
  arrange(desc(rsq_median)) |> 
	slice_head(n = 1) |> 
	pull(id) |> 
	as.numeric()

# contacts only
id_contacts <- err_tbl |> 
  filter(feature_version == "features_contacts") |> 
  arrange(desc(rsq_median)) |> 
	slice_head(n = 1) |> 
	pull(id) |> 
	as.numeric()

# communications only
id_communications <- err_tbl |> 
  filter(feature_version == "features_communications") |> 
  arrange(desc(rsq_median)) |> 
	slice_head(n = 1) |> 
	pull(id) |> 
	as.numeric()
```

```{r}
# best baseline model
id_baseline <- err_tbl |> 
  filter(feature_version == "features_baseline") |> 
  arrange(desc(rsq_median)) |> 
	slice_head(n = 1) |> 
	pull(id) |> 
	as.numeric()

# add in contacts features
id_contacts <- err_tbl |> 
  filter(feature_version == "features_contacts_full") |> 
  arrange(desc(rsq_median)) |> 
	slice_head(n = 1) |> 
	pull(id) |> 
	as.numeric()

# add in communication features
id_communications <- err_tbl |> 
  filter(feature_version == "features_communications_full") |> 
  arrange(desc(rsq_median)) |> 
	slice_head(n = 1) |> 
	pull(id) |> 
	as.numeric()

# full model
id_full <- err_tbl |> 
  filter(feature_version == "features_combined_full") |> 
  arrange(desc(rsq_median)) |> 
	slice_head(n = 1) |> 
	pull(id) |> 
	as.numeric()
```

```{r}
err_tbl |> 
  filter(id %in% c(id_full, id_ablate_contacts, id_ablate_communications, 
                   id_ablate_contacts_communications, id_contacts, 
                   id_communications)) |> 
  print_kbl()
```


### Interpretations

**Regression Coefficients**

```{r}
best_models[[id_full]] |> 
  tidy() |> 
  arrange(desc(abs(estimate))) |> 
  print_kbl()

best_models[[id_ablate_contacts]] |>
  tidy() |> 
  arrange(desc(abs(estimate))) |> 
  print_kbl()

best_models[[id_ablate_communications]] |>
  tidy() |> 
  arrange(desc(abs(estimate))) |> 
  print_kbl()

best_models[[id_ablate_contacts_communications]] |>
  tidy() |> 
  arrange(desc(abs(estimate))) |>
  print_kbl()

best_models[[id_contacts]] |> 
  tidy() |> 
  arrange(desc(abs(estimate))) |> 
  print_kbl()

best_models[[id_communications]] |> 
  tidy() |> 
  arrange(desc(abs(estimate))) |> 
  print_kbl()
```

**Feature Importance**

```{r}
predict_wrapper <- function(model, newdata) {
  predict(model, newdata) |> 
    pull(.pred)
}

get_shaps <- function(df1){
  predict_parts(explain_full, 
                new_observation = df1,
                type = "shap",
                B = 25) |> 
    filter(B == 0) |> 
    select(variable_name, variable_value, contribution) |> 
    as_tibble()
}

```

```{r}
rec_baseline <- recipe(lapse ~ ., data = features_baseline) |> 
      step_impute_median(all_numeric_predictors()) |> 
      step_impute_mode(all_nominal_predictors()) |>
      step_dummy(all_nominal_predictors()) |> 
      step_zv(all_predictors()) |> 
      step_nzv(all_predictors()) |>
      step_normalize(all_numeric_predictors())
feat_baseline <- rec_baseline |> prep(features_baseline) |> bake(new_data = NULL)

rec_contacts <- recipe(lapse ~ ., data = features_contacts) |> 
      step_select(-starts_with("n_")) |> 
      step_impute_median(all_numeric_predictors()) |> 
      step_impute_mode(all_nominal_predictors()) |>
      step_dummy(all_nominal_predictors()) |> 
      step_zv(all_predictors()) |> 
      step_nzv(all_predictors()) |>
      step_normalize(all_numeric_predictors())
feat_contacts <- rec_contacts |> prep(features_contacts) |> bake(new_data = NULL)

rec_communications <- recipe(lapse ~ ., data = features_communications) |> 
      step_select(-starts_with("n_")) |> 
      step_impute_median(all_numeric_predictors()) |> 
      step_impute_mode(all_nominal_predictors()) |>
      step_dummy(all_nominal_predictors()) |> 
      step_zv(all_predictors()) |> 
      step_nzv(all_predictors()) |>
      step_normalize(all_numeric_predictors())
feat_communications <- rec_communications |> prep(features_communications) |> bake(new_data = NULL)

rec_full <- recipe(lapse ~ ., data = features_combined) |> 
      step_select(-starts_with("n_")) |> 
      step_impute_median(all_numeric_predictors()) |> 
      step_impute_mode(all_nominal_predictors()) |>
      step_dummy(all_nominal_predictors()) |> 
      step_zv(all_predictors()) |> 
      step_nzv(all_predictors()) |>
      step_normalize(all_numeric_predictors())
feat_full <- rec_full |> prep(features_combined) |> bake(new_data = NULL)
```

**baseline**

```{r}
explain_full <- explain_tidymodels(best_models[[id_baseline]],  
                                   data = feat_baseline |> select(-lapse), 
                                   y = feat_baseline$lapse, 
                                   predict_function = predict_wrapper)

local_shap_baseline <- feat_baseline |>
  select(-lapse) |> 
  mutate(id = row_number()) |>
  nest(.by = id, .key = "dfs") |> 
  mutate(shaps = map(dfs, \(df1) get_shaps(df1))) |> 
  select(-dfs) |>
  unnest(shaps)

# local_shap_baseline <- local_shap_baseline |> 
#   mutate(variable_name = case_when(
#     str_detect(variable_name, "demo_educ") ~ "demo_education",
#     str_detect(variable_name, "demo_marital") ~ "demo_marital_status",
#     str_detect(variable_name, "demo_race") ~ "demo_race",
#     str_detect(variable_name, "demo_sex") ~ "demo_sex",
#     str_detect(variable_name, "_support") ~ "prop_social_support",
#     str_detect(variable_name, "drinker") ~ "prop_drink_status",
#     str_detect(variable_name, "drank") ~ "prop_drink_history",
#     str_detect(variable_name, "drink_future") ~ "prop_drink_presence",
#     variable_name %in% c("prop_pleasant", "prop_unpleasant", "prop_neutral",
#                          "prop_mixed_exp") ~ "prop_affect_exp",
#     variable_name == "prop_recovery" ~ "prop_know_recovery",
#     TRUE ~ variable_name
#   ))

local_shap_baseline |>
  mutate(contribution = abs(contribution)) |>
  group_by(variable_name) |>
  summarize(mean_shap = mean(contribution)) |>
  arrange(desc(mean_shap)) |>
  mutate(variable_name = factor(variable_name),
         variable_name = fct_reorder(variable_name, mean_shap)) |>
  ggplot(aes(x = variable_name, y = mean_shap)) +
  geom_point() +
  coord_flip()
```

**contacts**

```{r}
explain_full <- explain_tidymodels(best_models[[id_contacts]],  
                                   data = feat_contacts, 
                                   y = features_contacts$lapse, 
                                   predict_function = predict_wrapper)

local_shap_contacts <- feat_contacts |>
  select(-lapse) |> 
  mutate(id = row_number()) |>
  nest(.by = id, .key = "dfs") |> 
  mutate(shaps = map(dfs, \(df1) get_shaps(df1))) |> 
  select(-dfs) |>
  unnest(shaps)

# local_shap_contacts <- local_shap_contacts |> 
#   mutate(variable_name = case_when(
#     str_detect(variable_name, "demo_educ") ~ "demo_education",
#     str_detect(variable_name, "demo_marital") ~ "demo_marital_status",
#     str_detect(variable_name, "demo_race") ~ "demo_race",
#     str_detect(variable_name, "demo_sex") ~ "demo_sex",
#     str_detect(variable_name, "_support") ~ "prop_social_support",
#     str_detect(variable_name, "drinker") ~ "prop_drink_status",
#     str_detect(variable_name, "drank") ~ "prop_drink_history",
#     str_detect(variable_name, "drink_future") ~ "prop_drink_presence",
#     variable_name %in% c("prop_pleasant", "prop_unpleasant", "prop_neutral",
#                          "prop_mixed_exp") ~ "prop_affect_exp",
#     variable_name == "prop_recovery" ~ "prop_know_recovery",
#     TRUE ~ variable_name
#   ))

local_shap_contacts |>
  mutate(contribution = abs(contribution)) |>
  group_by(variable_name) |>
  summarize(mean_shap = mean(contribution)) |>
  arrange(desc(mean_shap)) |>
  mutate(variable_name = factor(variable_name),
         variable_name = fct_reorder(variable_name, mean_shap)) |>
  ggplot(aes(x = variable_name, y = mean_shap)) +
  geom_point() +
  coord_flip()
```

**communications**

```{r}
explain_full <- explain_tidymodels(best_models[[id_communications]],  
                                   data = feat_communications, 
                                   y = features_communications$lapse, 
                                   predict_function = predict_wrapper)

local_shap_communications <- feat_communications |>
  select(-lapse) |> 
  mutate(id = row_number()) |>
  nest(.by = id, .key = "dfs") |> 
  mutate(shaps = map(dfs, \(df1) get_shaps(df1))) |> 
  select(-dfs) |>
  unnest(shaps)

# local_shap_communications <- local_shap_communications |> 
#   mutate(variable_name = case_when(
#     str_detect(variable_name, "demo_educ") ~ "demo_education",
#     str_detect(variable_name, "demo_marital") ~ "demo_marital_status",
#     str_detect(variable_name, "demo_race") ~ "demo_race",
#     str_detect(variable_name, "demo_sex") ~ "demo_sex",
#     str_detect(variable_name, "_support") ~ "prop_social_support",
#     str_detect(variable_name, "drinker") ~ "prop_drink_status",
#     str_detect(variable_name, "drank") ~ "prop_drink_history",
#     str_detect(variable_name, "drink_future") ~ "prop_drink_presence",
#     variable_name %in% c("prop_pleasant", "prop_unpleasant", "prop_neutral",
#                          "prop_mixed_exp") ~ "prop_affect_exp",
#     variable_name == "prop_recovery" ~ "prop_know_recovery",
#     TRUE ~ variable_name
#   ))

local_shap_communications |>
  mutate(contribution = abs(contribution)) |>
  group_by(variable_name) |>
  summarize(mean_shap = mean(contribution)) |>
  arrange(desc(mean_shap)) |>
  mutate(variable_name = factor(variable_name),
         variable_name = fct_reorder(variable_name, mean_shap)) |>
  ggplot(aes(x = variable_name, y = mean_shap)) +
  geom_point() +
  coord_flip()
```


**full**

```{r}
explain_full <- explain_tidymodels(best_models[[id_full]],  
                                   data = feat_full, 
                                   y = feat_full$lapse, 
                                   predict_function = predict_wrapper)

local_shap_full <- feat_full |>
  select(-lapse) |> 
  mutate(id = row_number()) |>
  nest(.by = id, .key = "dfs") |> 
  mutate(shaps = map(dfs, \(df1) get_shaps(df1))) |> 
  select(-dfs) |>
  unnest(shaps)

# local_shap_full <- local_shap_full |> 
#   mutate(variable_name = case_when(
#     str_detect(variable_name, "demo_educ") ~ "demo_education",
#     str_detect(variable_name, "demo_marital") ~ "demo_marital_status",
#     str_detect(variable_name, "demo_race") ~ "demo_race",
#     str_detect(variable_name, "demo_sex") ~ "demo_sex",
#     str_detect(variable_name, "_support") ~ "prop_social_support",
#     str_detect(variable_name, "drinker") ~ "prop_drink_status",
#     str_detect(variable_name, "drank") ~ "prop_drink_history",
#     str_detect(variable_name, "drink_future") ~ "prop_drink_presence",
#     variable_name %in% c("prop_pleasant", "prop_unpleasant", "prop_neutral",
#                          "prop_mixed_exp") ~ "prop_affect_exp",
#     variable_name == "prop_recovery" ~ "prop_know_recovery",
#     TRUE ~ variable_name
#   ))

local_shap_full |>
  mutate(contribution = abs(contribution)) |>
  group_by(variable_name) |>
  summarize(mean_shap = mean(contribution)) |>
  arrange(desc(mean_shap)) |>
  mutate(variable_name = factor(variable_name),
         variable_name = fct_reorder(variable_name, mean_shap)) |>
  ggplot(aes(x = variable_name, y = mean_shap)) +
  geom_point() +
  coord_flip()
```

### Bayesian Comparison

```{r}
metrics_full <- best_config_metrics(fits_lst[[id_full]], metric = "rsq")
metrics_ablate_contacts <- best_config_metrics(fits_lst[[id_ablate_contacts]], 
                                               metric = "rsq")
metrics_ablate_communications <- best_config_metrics(fits_lst
                                                     [[id_ablate_communications]], metric = "rsq")
metrics_ablate_contacts_communications <- best_config_metrics(fits_lst
                                                              [[id_ablate_contacts_communications]], 
                                                              metric = "rsq")
metrics_contacts <- best_config_metrics(fits_lst[[id_contacts]], metric = "rsq")
metrics_communications <- best_config_metrics(fits_lst[[id_communications]], metric = "rsq")
```

#### Full and Ablated Model

```{r}
set.seed(101)

pp <- metrics_full |>
  select(id, id2, .estimate) |>
  mutate(.estimate = pmin(pmax(.estimate, 1e-6), 1 - 1e-6)) |>
  rename(full = .estimate) |>
  inner_join(
    metrics_ablate_contacts |>
      select(id, id2, .estimate) |>
      mutate(.estimate = pmin(pmax(.estimate, 1e-6), 1 - 1e-6)) |>
      rename(ablate_contacts = .estimate),
    by = c("id", "id2")
  ) |>
  inner_join(
    metrics_ablate_communications |>
      select(id, id2, .estimate) |>
      mutate(.estimate = pmin(pmax(.estimate, 1e-6), 1 - 1e-6)) |>
      rename(ablate_communications = .estimate),
    by = c("id", "id2")
  ) |>
  inner_join(
    metrics_ablate_contacts_communications |>
      select(id, id2, .estimate) |>
      mutate(.estimate = pmin(pmax(.estimate, 1e-6), 1 - 1e-6)) |>
      rename(ablate_both = .estimate),
    by = c("id", "id2")
  ) |>
  perf_mod(
    formula = statistic ~ model + (1 | id2/id),
    transform = tidyposterior::logit_trans,
    iter = 5000,
    chains = 4,
    adapt_delta = 0.9999,
    family = gaussian
  )
```

```{r}
pp_perf_tibble <- pp |>
  tidy(seed = 123) |>
  mutate(
    model = factor(
      model,
      levels = c(
        "full",
        "ablate_contacts",
        "ablate_communications",
        "ablate_both"
      )
    )
  ) |>
  group_by(model) |>
  summarize(
    pp_median = quantile(posterior, 0.5),
    pp_lower  = quantile(posterior, 0.025),
    pp_upper  = quantile(posterior, 0.975),
    .groups = "drop"
  ) |>
  arrange(model)

pp_perf_tibble
```

```{r}
pp_contrast <- tribble(
  ~model_1,               ~model_2,                 ~label,
  "full",                 "ablate_contacts",        "drop contacts",
  "full",                 "ablate_communications",  "drop communications",
  "full",                 "ablate_both",            "drop both"
) |>
  pmap_dfr(\(model_1, model_2, label) {
    draws <- pp |>
      contrast_models(list(model_2), list(model_1))
    
    draws |>
      summary(size = 0) |>
      mutate(
        probability = 1 - probability,
        contrast = label
      ) |>
      select(contrast, mean, lower, upper, probability) |>
      left_join(
        draws |>
          summarize(median = quantile(difference, 0.5)),
        by = character()
      ) |>
      select(contrast, median, everything())
  })

pp_contrast

```

```{r}
df_plot <- pp |>
  tidy(seed = 123) |>
  mutate(
    model = factor(
      model,
      levels = c("full", "ablate_contacts", "ablate_communications", "ablate_both"),
      labels = c(
        "Full model",
        "Ablate contacts",
        "Ablate communications",
        "Ablate contacts and communications"
      )
    )
  )

df_plot |>
  group_by(model) |>
  summarize(
    median = median(posterior),
    lower  = quantile(posterior, 0.025),
    upper  = quantile(posterior, 0.975),
    .groups = "drop"
  ) |>
  ggplot(aes(x = model, y = median)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  labs(x = NULL, y = "Posterior performance")
```

#### Contacts only, communications only models

```{r}
set.seed(101)

pp_2 <- metrics_contacts |>
  select(id, id2, .estimate) |>
  mutate(.estimate = pmin(pmax(.estimate, 1e-6), 1 - 1e-6)) |>
  rename(contacts = .estimate) |>
  inner_join(
    metrics_communications |>
      select(id, id2, .estimate) |>
      mutate(.estimate = pmin(pmax(.estimate, 1e-6), 1 - 1e-6)) |>
      rename(communications = .estimate),
    by = c("id", "id2")
  ) |>
  inner_join(
    metrics_ablate_contacts_communications |>
      select(id, id2, .estimate) |>
      mutate(.estimate = pmin(pmax(.estimate, 1e-6), 1 - 1e-6)) |>
      rename(id_demo = .estimate),
    by = c("id", "id2")
  ) |>
  perf_mod(
    formula = statistic ~ model + (1 | id2/id),
    transform = tidyposterior::logit_trans,
    iter = 5000,
    chains = 4,
    adapt_delta = 0.9999,
    family = gaussian
  )
```

```{r}
pp_perf_tibble_2 <- pp_2 |>
  tidy(seed = 123) |>
  mutate(
    model = factor(
      model,
      levels = c(
        "id_demo",
        "contacts",
        "communications"
      )
    )
  ) |>
  group_by(model) |>
  summarize(
    pp_median = quantile(posterior, 0.5),
    pp_lower  = quantile(posterior, 0.025),
    pp_upper  = quantile(posterior, 0.975),
    .groups = "drop"
  ) |>
  arrange(model)

pp_perf_tibble_2
```

```{r}
pp_contrast_2 <- tribble(
  ~model_1,          ~model_2,           ~label,
  "id_demo",         "communications",   "id_demo vs. communications",
  "id_demo",         "contacts",         "id_demo vs. contacts",
  "communications",  "contacts",         "communications vs. contacts"
) |>
  pmap_dfr(\(model_1, model_2, label) {
    draws <- pp_2 |>
      contrast_models(list(model_2), list(model_1))
    
    draws |>
      summary(size = 0) |>
      mutate(contrast = label) |>
      select(contrast, mean, lower, upper, probability) |>
      left_join(
        draws |>
          summarize(median = quantile(difference, 0.5)),
        by = character()
      ) |>
      select(contrast, median, everything())
  })

pp_contrast_2

```

```{r}
df_plot_2 <- pp_2 |>
  tidy(seed = 123) |>
  mutate(
    model = factor(
      model,
      levels = c("id_demo", "contacts", "communications"),
      labels = c(
        "ID + demographics",
        "Contacts",
        "Communications"
      )
    )
  )

df_plot_2 |>
  group_by(model) |>
  summarize(
    median = median(posterior),
    lower  = quantile(posterior, 0.025),
    upper  = quantile(posterior, 0.975),
    .groups = "drop"
  ) |>
  ggplot(aes(x = model, y = median)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  labs(x = NULL, y = "Posterior performance")
```














